Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-09-24 main_new.tex
Updates from Overleaf

Traditional data collection at sea has typically been based on static
buoys, lagrangian float,s or ship-based methods, with significant
logistical limitations that directly impact coverage and sampling
resolution. Modern methods using satellite remote-sensing provide
large-scale coverage, but have limited resolution, are limited to
sensing the surface of the ocean, and are impacted by cloud cover. The
advent of robust mobile robotic platforms \cite{Bellingham07} has
resulted in significant contributions to environmental monitoring and
sampling. In particular, autonomous underwater vehicles (AUVs), have made
strides in advancing the state of sampling and consequently have made
robotics an integral part of ocean observation in large part by our own
work % driven by
% using statistical methods in design and data assimilation
\citep{das11b,Graham2013,Das2015,das15,fossuminformation,fossum18b}.
Others include \cite{wikle2013modern} focusing on hierarchical
statistical models, \cite{sahu2008space} which studies spatio-temporal
models for sea surface temperature and salinity data, while
\cite{mellucci2018oceanic} looks at the statistical prediction of
features using an underwater glider. Common to these approaches is the
use of information-based methods to infer environmental sampling and overcome common challenges, namely:

\begin{itemize}
\item Static sampling paths fail to capture necessary features in dynamic ocean conditions. Incontrast, these approaches make decisions about where to sample  sequentially, i.e.  
  recently acquired information can be assimilated and used to improve
  statistical models and reduce uncertainty associated with where to make measurements.
\item As a priori information about the state of the ocean is very
  uncertain, there is a substantial efficiency gain in reacting to
  information obtained from measurements taken \emph{in-situ}; this is
  usually referred to as the \emph{adaptivity gap} \citep{Krause2008phd}.
\item For such types of sampling problems, the number of choices (i.e.
  locations, trajectories, and candidate designs) makes the problem
  combinatorially large, creating a trade-off between optimization
  (finding the optimal design) and computability (arriving at a
  solution in reasonable time), which has to be considered in
  practice.
\end{itemize}{}

The combination of statistical tools and robotic platforms is a
natural symbiosis which enables information-based sensing. Central to
this is the ability to model spatially correlated variables and
provide formal measures of uncertainty. By far the most practical
models use Gaussian processes (GPs), which will also be used in our
formulation, in large part because it allows efficient implementation
and evaluation, in turn enabling prioritization of sampling efforts to
be formalized into decision making systems on-board a robotic
platform.

>>>>

Traditional data collection at sea has typically been based on static
buoys, lagrangian floats or ship-based methods, with significant
logistical limitations that directly impact coverage and sampling
resolution. Modern methods using satellite remote-sensing provide
large-scale coverage, but have limited resolution, are limited to
sensing the surface of the ocean, and are impacted by cloud cover. The
advent of robust mobile robotic platforms \cite{Bellingham07} has
resulted in significant contributions to environmental monitoring and
sampling. In particular, autonomous underwater vehicles (AUVs), have made
strides in advancing the state of sampling and consequently have made
robotics an integral part of ocean observation; our own work
has contributed to this effort.

% using statistical methods in design and data assimilation
\citep{das11b,Graham2013,Das2015,das15,fossuminformation,fossum18b}.
Others include \cite{wikle2013modern} focusing on hierarchical
statistical models, \cite{sahu2008space} which studies spatio-temporal
models for sea surface temperature and salinity data, while
\cite{mellucci2018oceanic} looks at the statistical prediction of
features using an underwater glider. Common to these approaches is the
use of information-based methods to infer environmental sampling and overcome common challenges, namely:

\begin{itemize}
\item Decisions on where to sample happen sequentially, i.e.  how
  recently acquired information can be assimilated and used to improve
  statistical models and reduce uncertainty associated with where to make measurements.
\item As a priori information about the state of the ocean is very
  uncertain, there is a substantial efficiency gain in reacting to
  information obtained from measurements taken \emph{in-situ}; this is
  usually referred to as the \emph{adaptivity gap} \citep{Krause2008phd}.
\item For such types of sampling problems, the number of choices (i.e.
  locations, trajectories, and candidate designs) makes the problem
  combinatorially large, creating a trade-off between optimization (finding the most resource-efficient design to collect necessary data), and computability (arriving at a
  solution in reasonable time), which has to be considered in
  practice.
\end{itemize}{}

The combination of statistical tools and robotic platforms is a
natural symbiosis which enables information-based sensing. Central to
this is the ability to model spatially-correlated variables and
provide formal measures of uncertainty. By far the most practical
models use Gaussian processes (GPs), which will also be used in our
formulation, in large part because they allow efficient implementation
and evaluation, in turn enabling prioritization of sampling efforts to
be formalized into decision making systems on-board a robotic
platform.
